Edge sign prediction in general graphs and Correlation Clustering

### 2017-12-02 cc/cc_main.tex
reorganize non worst case CC and add two more refs
typos and stability in cc
review gtx description and experiments
in particular, avoid mentioning strech by name, and say we only have a
conjecture regarding the runtime
also make the transition between cc and gtx smoother

\subsection{Variants and extensions}
\label{sub:variants_and_extensions}
\input{cc_variants}

\subsubsection{\pcc{} under stability assumption}
\label{ssub:cc_under_stability_assumption}
\input{cc_multimincut_stable}

>>>>

\subsection{Beyond worst case instances}
\label{sub:cc_non_worst_case}

\input{cc_non_worst_case}

\begin{aside}
\subsection{Variants and extensions}
\label{sub:variants_and_extensions}
\input{cc_variants}
\end{aside}

Let us review this material about \pcc{} in the light of our thesis objective: efficiently and
accurately characterize edges in complex networks, or rather signed graphs in this chapter. The
results on the hardness of \pcc{}, and the fact that the best approximations rely on a linear
program with a large number of constraints seems to run counter to such efficiency and accuracy
requirements. To avoid this pitfall, we presented many existing heuristics. More importantly, recall
that our learning bias is that nodes are assigned to $K$ groups, and that signs are consistent
with those groups. Informally, the closer an input signed graph is to this ideal situation, the more
regular it is with respect to this bias, and thus the easier the \esp{} problem is. Accordingly, the
works described in \autoref{sub:cc_non_worst_case} point out that such non worst case instances are
indeed where we expect clustering algorithms to be able to identify those $K$ groups with little to
no error. In the next section, we present an algorithm relying on a similar intuition, in an active
setting and where $K=2$.
